---
title: "google trends_example with"
author: "Imgesu Cetin"
date: "7/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Google Trends Index:

Google Trends is an online based and freely accessible application that provides the frequency with which the given query has been entered in the Google Search in relation to the total search volume.

Each data point is divided by the total searches of the geography and time range it represents to compare relative popularity.This means that when we look at search interests over time for a topic, we’re looking at interests as a proportion of all searches on all topics on Google at the time and location.



```{r}
#setting up work environment

data("countries")
data("categories")
library(gtrendsR) 
library(tidyverse)
library(lubridate)

#categories that we can use.
#202	Visa & Immigration id code is=	555
#Immigration Policy & Border Issues	1313
```

# Trying with two origin countries, Syria and Iraq, two destination countries, Turkey and Germany.

# For Origin Country Syria:
```{r}
#with the keyword 'Germany' for the geolocation of Syria, for all time, which is ever since 2004
#arabic iso language code is 'ar'
#
res<-gtrends('germany',geo=c("SY"),time='all',category = 555,hl='ar')
plot(res)
#when using a catagory for this code with out making it arabic it didn't work. when i changed to hl='ar' it worked. 
```

```{r}
#keyword 'Turkey'(destination) for Syria(origin) for the catagory of Visa and immigration
res<-gtrends('turkey',geo=c("SY"),time='all',category = 555,hl='ar')
plot(res)

#when I put 'go to Turkey' it didn't work. However, when I put, 'Turkey' it works.

```

```{r}
#keyword 'Turkey'(destination) for Syria(origin) for the catagory of Visa and immigration, when they search it in english, default version
res<-gtrends('turkey',geo=c("SY"),time='all',category = 555)
plot(res)

#looks the same as when I change the language to arabic,
```

```{r}
#sentences do not work for origin country Syria

#"migrate to Turkey"
#"go to Turkey" do not work
#"immigrate to Turkey'

res<-gtrends('immigrate to turkey',geo=c("SY"),time='all',hl='ar')
plot(res)
#when I changed the dates to defa

#I put the same code, and I did not get the same information?

```
```{r}
#when I add both the keywords "Germany" and "Turkey"(both destination countries) for geolocation of "Syria"(orgin country) for the catagory of visa and migration, and when the language code is 'arabic'

res<-gtrends(c('turkey','germany'),geo=c("SY"),time='all',category = 555 ,hl='ar')
plot(res)

#when both keywords, germany and turkey are used, we can see that germany has a higher hit proportion compared to Turkey for the orgin country Syria
```

```{r}
#when I add both the keywords "Germany" and "Turkey"(both destination countries) for geolocation of "Syria"(orgin country) for the catagory of visa and migration, and when the language code is 'english'.

res<-gtrends(c('turkey','germany'),geo=c("SY"),time='all')
plot(res)

#gives the same results as when the lanugae code was 'arabic'
#howver when I change the catagory I see that there is alot of volitility, this may be becayse searches for 'germany' and ;turkey' maybe searched in other motives aside for migration purposes. 
```

```{r}
res<-gtrends(c('germany'),geo=c("SY"),time='all',onlyInterest = TRUE)
plot(res)

res
#doesn't change the hits.

```



```{r}
res<-gtrends(c('turkey'),geo=c("SY"),time='all')
plot(res)
```

# For Origin Country Iraq:

```{r}

```


```{r}
#for origin country Iraq, when keyword is Turkey for All catagories.
#for time all and no language
res<-gtrends('turkey',geo=c("IQ"), time ="all")
plot(res)

```


```{r}
#for origin country Iraq, when keyword is Turkey for the catagory of Visa and Immigration and when language is English.
res<-gtrends(c('turkey','germany'),geo=c("IQ"),time='all',hl='ar',category = 555)
plot(res)


#nothing for when language is default at english. 
```

```{r}
#for origin country Iraq, when keyword is Turkey for the catagory of Visa and Immigration and when language is Arabic.

res<-gtrends('turkey',geo=c("IQ"),time='all',category = 555,hl='ar')
plot(res)

#some kind of influence of trends for migration? There is a spike after 2013?
res
```

#for Germany
```{r}
#using 'go to germany' does work 

res<-gtrends('go to germany',geo=c("IQ")
plot(res)
```


```{r}
#for origin country Iraq, when keyword is Turkey for the catagory of Visa and Immigration and when language is Arabic.

res<-gtrends('germany',geo=c("IQ"),time='all',category = 555,hl='ar')
plot(res)

#some kind of influence of trends for migration? There is a spike after 2013?
```

```{r}
#looking at the data
head(res)
```

```{r}
#for the keyword 'germany' when we do not limit to catagories of Visa and Immigration
res<-gtrends('gotogermany',geo=c("IQ"))

```


```{r}
#comparing keyword 'germany' to 'turkey' for all catagories on the web for all time.

res<-gtrends(c('germany','turkey'),geo=("SY"),time=("2010-01-02 2019-01-01"),category = c(555))

plot(res)

#use both catagories that make sence
```


#Aggregating for each year for origin country Iraq for search terms Germany and Turkey with the category of Visa and Immigration
```{r}

res<-gtrends(c('germany','turkey'),geo=c("IQ"),time='all', category = 555, hl='ar')
plot(res)

timeseries <- as_tibble(res$interest_over_time) %>% 
  mutate(date = ymd(date)) %>% # CONVERT DATE FORMAT
  filter(date < Sys.Date() - 7)# taking out the past 7 days.


#looking at the data after getting it cleaned up
timeseries
#seperating date
timeseries<-separate(timeseries, "date", c("Year", "Month", "Day"), sep = "-")

timeseries
#taking aggregate for the years

#basic plot to show over the years, it seems as though there is an steady increase after 2010-2015
newtimeseries<-aggregate(hits ~ Year+keyword+geo, data=timeseries,median)

newtimeseries


```
#ploting new aggregated yearly data

```{r}
library(ggplot2)
str(newtimeseries)
#creating plot
newtimeseries%>%
  ggplot()+geom_point(aes(x=Year, y=hits, color=keyword), size=1)+ scale_y_continuous(limits = c(0,100)) + scale_color_brewer(palette = 'Set2') + theme_bw() + labs(x = NULL,y ="Relative Search Interest", color = NULL, title = "Google Trends: Interet over time for origin country US")

```

# Forecasting
https://www.christopheryee.org/blog/mining-google-trends-data-with-r-featuring-gtrendsr/

This is a good website to check out for forecasting google trend searches

```{r}
#I used prophet for easy forecastin. We can expand with other methods.
install.packages('prophet')
library(prophet)

#Prophet is a procedure for forecasting time series data based on an additive model where non-linear trends are fit with yearly, weekly, and daily seasonality, plus holiday effects. It works best with time series that have strong seasonal effects and several seasons of historical data. Prophet is robust to missing data and shifts in the trend, and typically handles outliers well.

```

# for simple computation I have used US as origin and CANADA as destination. As an english speaking country, we are able to search 
```{r}

res<-gtrends(c('migrate to canada','migrate to mexico'),geo=c("US"),time='all')
plot(res)


```
# cleaning up dataframe
```{r}
timeseries <- as_tibble(res$interest_over_time) %>% 
  mutate(date = ymd(date)) %>% # CONVERT DATE FORMAT
  filter(date < Sys.Date() - 7) # REMOVE "NOISY" DATA FROM LAST SEVEN DAYS

```

#graph over time
```{r}
timeseries %>% 
  ggplot() +
  geom_line(aes(date, hits, color = keyword), size = 1) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_color_brewer(palette = 'Set2') +
  theme_bw() +
  labs(x = NULL,
       y = "Relative Search Interest",
       color = NULL,
       title = "Google Trends: interest over time (US)")
```

```{r}

```

