---
title: "app example Rmd_imgesu"
author: "Imgesu Cetin"
date: "8/22/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#data 
library(shiny)
library(plotly)
library(gtrendsR)
library(readr)
asylum<-read.csv('asylumdata_new.csv')
#source("Function_Rshiny.R")
library(shinydashboard)
data("countries")
Migrationdata<-read.csv('migrationdata_new.csv')
library(readxl)
iso<- read_excel("iso_country_lang_data.xlsx")


#standardize country names 
library(StandardizeText)
Migrationdata$origin.stand<-standardize.countrynames(Migrationdata$Country.of.birth.nationality,standard="iso",suggest="auto")
Migrationdata$destination.stand<-standardize.countrynames(Migrationdata$Country,standard="iso",suggest="auto")
#asylum data
asylum$origin.stand<-standardize.countrynames(asylum$Country.of.origin,standard="iso",suggest="auto")

asylum$destination.stand<-standardize.countrynames(asylum$Country.of.asylum,standard="iso",suggest="auto")

unique(Migrationdata$origin.stand)
write.csv(Migrationdata,"migrationdata_new.csv")
write.csv(asylum,"asylumdata_new.csv")
#the new variables are origin.stand and destination.stand
```
```{r}
unique(asylum$origin.stand)
unique(Migrationdata$destination.stand)
#there is only 36 unique country names for the migration destination
```

```{r}
#Function
###############################################################
library(gtrendsR)
library("dplyr")
library("stringr")
library(ggplot2)
library("tidyverse")
library(ggpubr)

###############################################################


# rm(list = ls())
# normalize to scale 0-100
normalized <- function(x){
  ((x-min(x))/(max(x)-min(x)))*100
}



####################  Total migration OECD  ####################
# Migration total - OECD
#Migrationdata <- read_csv("migrationdata_new.csv")
Migrationdata$Year<- as.integer(Migrationdata$Year)
# Function for Aggregating and filtering the Migration data.
Agg_filter_migration <- function(Migrationdata, origin,
                                destination, Year_from, Year_till){
  # Detect the Inflows and aggregate
  Migrationdata_agg <- Migrationdata %>%  
    filter(str_detect(Variable, "^Inflows")) %>% 
    group_by(origin.stand, destination.stand, Year) %>% 
    summarise(Value = sum(Value))
  # Filter by country of origin and destination
  mig_data_1 <- Migrationdata_agg %>%  
    filter(origin.stand == origin,
           destination.stand == destination,
           Year > Year_from, Year < Year_till)
  # Normalize the migration data into 0-100 scale.
  mig_data_2 <- mig_data_1 %>%  ungroup() %>% 
    select(Year, Value) %>%
    mutate_if(is.integer, as.character) %>% 
    mutate(migration_flow_total = normalized(Value)) %>% 
    select(-Value)
  
  return(mig_data_2)
  
}
# This also works
#A<-Agg_filter_migration(Migrationdata, origin="Turkey",
#                                destination="Germany", Year_from=2001, Year_till=2014)

######################### Asylum OECD   ####################
# Function for Aggregating and filtering the Asylum-OECD
Agg_filter_OECDasylum <- function(Migrationdata, origin,
                                 destination, Year_from, Year_till){
  # Detect the Inflows and aggregate
  Asylum_OEDC <-  Migrationdata %>% 
    filter(str_detect(Variable, "^Inflows of asylum")) %>% 
    group_by(origin.stand, destination.stand, Year) %>% 
    summarise(Value = sum(Value))
  
  # Filter by country of origin and destination
  Asylum_OEDC_1 <- Asylum_OEDC %>%  
    filter(origin.stand == origin,
           destination.stand == destination,
           Year > Year_from, Year < Year_till)
  
  # Normalize the migration data into 0-100 scale.
  Asylum_OEDC_2 <- Asylum_OEDC_1 %>%  ungroup() %>% 
    select(Year, Value) %>%
    mutate_if(is.integer, as.character) %>% 
    mutate(Asylum_OEDC = normalized(Value)) %>% 
    select(-Value)
  
  return(Asylum_OEDC_2)
  
}
#This also works
#D<-Agg_filter_OECDasylum(Migrationdata, origin="Turkey",
 #                                destination="Germany", Year_from=2000, Year_till=2015)

########################## Asylum - UNHCR ###################
#asylum<-read.csv("asylum-applications_data.csv")
#asylum <- read.csv("asylumdata_new.csv")

Agg_UNHCR_asylum<- function(asylum, origin_asylum,
                            destination_asylum){
  
  # Detect the Inflows and aggregate
  Asylum_UNHCR_agg<-asylum%>%
    group_by(origin.stand , destination.stand , Year) %>%
    summarise(Value_asylum=sum(applied))
  
  # Filter by country of origin and destination
  aslyum_UNHCR_1 <- Asylum_UNHCR_agg %>%  
    filter(origin.stand == origin_asylum,
           destination.stand == destination_asylum)
  
  # Normalize the migration data into 0-100 scale.
  aslyum_UNHCR_2 <- aslyum_UNHCR_1 %>% ungroup() %>% 
    select(Year, Value_asylum) %>%
    mutate(Year = as.character(Year),
           Asylum_UNHCR = normalized(Value_asylum)) %>% 
    select(-Value_asylum)
  
  return(aslyum_UNHCR_2)
  
}
#this works
# C <- Agg_UNHCR_asylum(asylum,
#                  "Turkey",
#                  "Germany")
######################## Migration flows Data frame ################
Migration_DT <- function(Migrationdata, asylum,
                         origin,destination,
                         Year_from,Year_till,
                         origin_asylum, destination_asylum){
  
  Migration_OECD <- Agg_filter_migration(Migrationdata, origin,
                                         destination, Year_from, Year_till)
  
  Asylum_OECD <- Agg_filter_OECDasylum(Migrationdata, origin,
                                      destination, Year_from, Year_till)
  
  Asuylum_UNHCR <- Agg_UNHCR_asylum(asylum,
                                    origin_asylum,
                                     destination_asylum)
  
  DT <- Migration_OECD %>% 
    left_join(Asylum_OECD, by = "Year") %>% 
    left_join(Asuylum_UNHCR, by = "Year")
  
  return(DT)
}
# This also works
#DT <- Migration_DT(Migrationdata,asylum,
 #             origin = "Turkey",destination = "Germany",
 #             Year_from = 2005,Year_till = 2018,
 #             origin_asylum = "Turkey",
  #            destination_asylum = "Germany")
# 



######################### Google trends data ######################

# Function for aggregating the GT data as yearly basis.
Agg_yearly <- function(GTdata){
  
  Yearly_data <- GTdata[[1]]  %>% 
    mutate(Year =str_extract(date, "^.{4}")) %>% 
    mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
    group_by(Year, geo) %>% 
    summarise(hits_average = mean(as.numeric(hits))) %>% ungroup()
  
  return(Yearly_data)
  
  
}

GT_dataframe <- function(serach_terms = NA, origin_code,
                                language = "en",
                                category =0){
  
  # Make a dataframe first.
  
  # Approach 1 (Destination as keywords, category as 555)
  GT_1<-gtrends(keyword = serach_terms,geo=c(origin_code), 
                category = category,
                time='2005-01-01 2017-12-31',hl=language,
                gprop = "web", onlyInterest = TRUE)
  GT_1_agg <- Agg_yearly(GT_1) %>% ungroup() %>%
    select(Year, hits_average) %>% 
    rename(Approach_1_hits = hits_average)
  # Approach 2 (Destination as keywords, without category)
  GT_2<-gtrends(keyword = serach_terms,geo=c(origin_code),
                time='2005-01-01 2017-12-31',hl=language,
                gprop = "web", onlyInterest = TRUE)
  GT_2_agg <- Agg_yearly(GT_2) %>% ungroup() %>%
    select(Year, hits_average) %>% 
    rename(Approach_2_hits = hits_average)
  # Aprroach 3 (Category as 555 Without any keywords)
  GT_3<-gtrends(geo=c(origin_code), 
                category = category,
                time='2005-01-01 2017-12-31',hl=language,
                gprop = "web", onlyInterest = TRUE)
  GT_3_agg <- Agg_yearly(GT_3) %>% ungroup() %>%
    select(Year, hits_average) %>% 
    rename(Approach_3_hits = hits_average)
  
  GT_data <- GT_1_agg %>% 
    left_join(GT_2_agg, by = "Year") %>% 
    left_join(GT_3_agg, by = "Year")
  
  return(GT_data)
}
# This works
# gtrentA <- GT_dataframe(serach_terms = 'Germany', origin_code = 'SY',
#          language = "ar",
 #         category = 555)
# 
# 

 
# 
# # full data frame
# DT_GT <- B %>% left_join(A, by = "Year")


# Generate the comparison dashboard

Dashboard_DT <- function(Migrationdata,asylum,
                      origin,destination,
                      Year_from,Year_till,
                      origin_asylum, destination_asylum,
                      serach_terms, origin_code,
                      language ,category){
  
  DT <- Migration_DT(Migrationdata, asylum,
                     origin,destination,
                     Year_from,Year_till,
                     origin_asylum, destination_asylum)
  
  # Google trends
  GT <- GT_dataframe(serach_terms, origin_code,
         language, category)
  
  # full dataframe
  DT_GT <- DT %>% left_join(GT, by = "Year")
  
  return(DT_GT)
  
  
}


# Visualization
Dashboard_plot <- function(DT_GT){
  # x axis scale
  Scale_x <- scale_x_continuous(breaks = waiver(), n.breaks = 7)
  # Migraiton total
  A <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y=migration_flow_total),color = "blue", group = 1) + 
    labs(title ="Migration Inflows", y = "", x= "") + 
    ylim(0,100) + Scale_x
  # Asylum OECD
  B <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y=Asylum_OEDC),color = "red", group = 1) +
    labs(title ="Asylum OECD", y = "",x= "", size = 8) + ylim(0,100)+ Scale_x
  # Asylum UNHCR
  C <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y=Asylum_UNHCR),color = "red", group = 1) +
    labs(title ="Asylum UNHCR", y = "",x= "") + 
    ylim(0,100) + xlim(2014,2017)
  
  ######## Google Trends ##########
  # Approach 1
  p <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y=Approach_1_hits),color = "Green", group = 1) +
    ylim(0,100) 
  # Approach 2
  q <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y = Approach_2_hits), color = "black",group = 1) +
    labs(y = "A2", x= "") + ylim(0,100)
  # Approach 3
  d <- ggplot(data=DT_GT, aes(x=as.integer(Year))) +
    geom_line(aes(y = Approach_3_hits), color = "navy",group = 1) +
    labs(y = "A3", x= "") + ylim(0,100)
  
  
  ggarrange(A,B,C,
            p +labs(y="A1", x= "")+ Scale_x,
            p +labs(y="", x= "")+ Scale_x,
            p + labs(y="", x= "") + xlim(2014,2017),
            q +labs(y="A2", x= "")+ Scale_x,
            q +labs(y="", x= "")+ Scale_x,
            q + labs(y="", x= "") + xlim(2014,2017),
            d +labs(y="A3", x= "")+ Scale_x,
            d +labs(y="", x= "")+ Scale_x,
            d + labs(y="", x= "") + xlim(2014,2017),
            heights = c(2, 2),
            ncol = 3, nrow = 4)
}

 DT_GT <- Dashboard_DT(Migrationdata, asylum,
           origin = "Turkey",destination = "Germany",
           Year_from = 2005,Year_till = 2018,
           origin_asylum = "Turkey",
           destination_asylum = "Germany",
           serach_terms = 'Germany', origin_code = 'TR',
           language = "en",category = 555)

Dashboard_plot(DT_GT)

DT_GT

########
#new function for maping by imgesu
############
#data
world<-map_data("world")
#top hits function
top.hits<- function(world,search_keyword,time){
  a<-gtrends(keyword = search_keyword,time = time)
  country.hits<-a$interest_by_country%>%
    filter(location %in% world$region, hits>0)%>%
    mutate(region = location, hits = as.numeric(hits))%>%
    select(region,hits)%>%
    ungroup()
  return(country.hits)
}

#top hits function with graph

top.hits.map <- function(country.hits){
  ggplot() +
  geom_map(data = world,
           map = world,
           aes(x = long, y = lat, map_id = region),
           fill="#ffffff", color="#ffffff", size=0.15) +
  geom_map(data = country.hits,
           map = world,
           aes(fill = hits, map_id = region),
           color="#ffffff", size=0.15) +
  scale_fill_continuous(low = 'grey', high = 'red') +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())
  
  
}

data<-top.hits(world,"migration","now 1-d")
top.hits.map(data)


data


```



```{r}
#install.packages("shinythemes")
library(shinythemes)
library(shiny)
library(plotly)
library(gtrendsR)
library(readr)
library(ggplot2)
library(dplyr)
library(DT)

##### user interface #############
ui<-fluidPage(theme = shinytheme("cerulean"),
    titlePanel("Google Trends Index for Forecasting Migration"),
    sidebarLayout(
      sidebarPanel(
        #select country
        selectInput("geo", label = h5("Select Origin Country for Google Trends"),
                    choices = unique(iso$iso), selected = "TR"),
        selectInput("lang", label=h5("Origin language"),choices= unique(iso$hl),selected = "en"),
          
        selectInput("queries", label = h5("Destination for Google Trends and Historic Data"),
                   choices=unique(asylum$destination.stand),selected = "Germany" ),

        selectInput("Migration.origin", label = h5("Data origin"),
                   choices=unique(asylum$origin.stand),selected = "Turkey" ),
        selectInput("migration.keyword", label = h5("Select Keyword for top hits globaly"),
                   choices=c("migration","asylum"),selected = "migration"),
           # br() element to introduce extra vertical spacing ----
                          # br(),
        #______ input to select for top hits around the world-------#
        
        
       selectInput("time.map", label = h5("Select time for top hits globally "),
                   choices = c("now 1-H",
                             "now 4-H"),
                   selected = "now 4-H")),

  #____________________________main panel output ____________________# 
    mainPanel( tabsetPanel(type = "tabs",
                           tabPanel("Plots", plotOutput("plot1",height=700)),
                           tabPanel("Top Hits Map",plotOutput("map"),DTOutput("mytable")),
                           tabPanel("Top Hits table",))
               
                      ) #ends main panel  
                   )#ends side bar part
            
        )#ends the fluid page
    




## server.R ##
library(shiny)
library(shinydashboard)
library(gtrendsR)
library(ggplot2)
library(stringr)
library(ggpubr)
library("dplyr")
library("stringr")
library("tidyverse")
library(ggpubr)


server<-function(input, output) {


    data("countries")
  #output of data table


  #this uses the newest function
   dataInput <- reactive({
     Dashboard_DT(Migrationdata,
                 asylum,
                 origin = input$Migration.origin,
                 destination = input$queries,
                 Year_from = 2005,
                 Year_till = 2018,
                 origin_asylum = input$Migration.origin,
                 destination_asylum = input$queries,
                 serach_terms = input$queries,
                 origin_code = input$geo,
                 language = input$lang,
                 category = 555)})

  #this uses the first original function
     # Generate_comparison(serach_terms = input$queries,
     #                      origin_code = input$geo,
     #                       language = input$lang,
      #                      origin = input$Migration.origin,
      #                      destination = input$Migration.destination,
       #                     origin_asylum = input$Asylum.origin,
       #                     destination_asylum = input$Asylum.destination)
   #plots our function of 12 plots
   output$plot1<- renderPlot({
     res<-dataInput()
     Dashboard_plot(res)
    
    
      
    })
   world<-map_data("world")
  # dataMap <- reactive({
  #   top.hits(world,
  #            search_keyword = input$migration.keyword,
  #               time = input$time.map,
  #               category = 555)
  #  })

  

     output$map <- renderPlot({
       a<-top.hits(world,
                search_keyword = input$migration.keyword,
                time = input$time.map)
       
  top.hits.map(a)
   })
   
   output$mytable <-renderDT({
     a<-top.hits(world,search_keyword = input$migration.keyword,
              time = input$time.map)
     a()
   })
    
}#ends server functioin

shinyApp(ui=ui,server = server)


```

```{r}

#visualizing map of intensity of search terms
library(dplyr)
library(ggplot2)
library(gtrendsR)
library(maps)
data('countries')
data('categories')

#ploting the world searches for all time according to the category of Visa and Immigration.
a <- gtrends(keyword = "asylum", time = "now 4-H",category = 555)

a$interest_by_country

a$interest_by_country
plot(a)

a$interest_by_country
```

```{r}

```

# plotting for the world


```{r}


plot

a$interest_by_region
world<-map_data("world")
world$region
#world data for our visualization
  a$interest_by_country %>%
    filter(location %in% world$region, hits>0) %>%
    mutate(region = location, hits = as.numeric(hits)) %>%
    select(region,hits) -> my_df

#res_world$interest_by_country %>%
 # filter(location %in% world$region, hits > 0) %>%
  #mutate(region = location, hits = as.numeric(hits)) %>%
  #select(region, hits) -> my_df
my_df%>%ggplot() +
  geom_map(data = world,
           map = world,
           aes(x = long, y = lat, map_id = region),
           fill="#ffffff", color="#ffffff", size=0.15) +
  geom_map(data = my_df,
           map = world,
           aes(fill = hits, map_id = region),
           color="#ffffff", size=0.15) +
  scale_fill_continuous(low = 'grey', high = 'red') +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())

#we can visualize this too see which countries are trending in searches for keywords regarding migration.
```

Notes:
change iso code into country name
have only origin, language and destination.
adding prediction, as check box

create a dataframe.

1) similarity score
*best performing score.
*
*
2) use national data sources for ground truth. For a couple of examples. 
  US/Germany-
  *adding a tab for comparing international data base and national data base
3) Prediction: Forecasting: checkbox to see 
4) Which countries are searching for migration the most, 
top 10 country 
*top keywords according to map
*compares google trends data
*New trends: Which countries are using the 

6) add get/pull data part in UI
*add
*taking out the category
*make it fancy

Notes August 31st______
1) normalization according to population in the data set?
2) adding worldwide to the searches plus adding data to our already made dataset, could get migration data for the world from World Bank. 

