---
title: "Functions_new_imgesu"
author: "Imgesu Cetin"
date: "8/12/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#preparing data
Migrationdata <- read.csv("migrationData.csv")
unique(Migrationdata$Variable)


Migrationdata %>% filter(str_detect(Variable, "^Inflows")) %>%
  distinct(VAR)
Migrationdata %>%  filter(VAR == "B13")

Migrationdata_agg <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))

#filtering OECD data for just asylum
Migrationdata_agg_asylum <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows of asylum")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value_asylum = sum(Value))



#asylum data from UNHCR. This data is incomplete
asylum_applications_UNHCR<-read_csv("asylum-applications_data.csv")


Asylum_UNHCR_agg<-asylum_applications_UNHCR%>%
  group_by(`Country of origin`,`Country of asylum`,Year) %>%
  summarise(Value_asylum=sum(applied))

str(Asylum_data_agg$Year)
str(Migrationdata_agg_asylum$Year)
str(Migrationdata$Year)
```


#Function
```{r}

Agg_yearly <- function(GTdata){
  
  Yearly_data <- GTdata[[1]]  %>% 
    mutate(Year =str_extract(date, "^.{4}")) %>% 
    mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
    group_by(Year, geo) %>% 
    summarise(hits_average = mean(as.numeric(hits))) %>% ungroup()
  
  return(Yearly_data)
  
  
}

# Funciton for Migration data filtering
Filtering_migration <- function(mig_data, origin,
                                destination, Year_from, Year_till){
  
  mig_data_New <- mig_data %>%  
    filter(Country.of.birth.nationality == origin,
           Country == destination,
           Year > Year_from, Year < Year_till)
  
  return(mig_data_New)
  
}
<<<<<<< HEAD

=======
>>>>>>> 9898f3adac67366e5d50a5a79b5f3e83723514fa

# Funciton for Assuylum filtering
Filtering_asylum<- function(Asylum_UNHCR_agg, origin_asylum,
                            destination_asylum){
  
  aslyum_data_New <- Asylum_UNHCR_agg %>%  
    filter(`Country of origin` == origin_asylum,
           `Country of asylum` == destination_asylum)
  
  return(aslyum_data_New)
  
}

# Generate the comparison plot
Generate_comparison <- function(serach_terms = NA, origin_code,
                                language = "en", origin,destination,
                                category =0,
                                origin_asylum, destination_asylum){
  
  # GT data
  GT<-gtrends(keyword = serach_terms,geo=c(origin_code), category = category,
              time='2004-01-01 2017-12-31',hl=language,
              gprop = "web", onlyInterest = TRUE)
  
  GT_year <- Agg_yearly(GT)  %>%
    ungroup() %>% 
    select(Year, hits_average)
  # Migration data
  Migration <- Filtering_migration(Migrationdata_agg,
                                   origin,
                                   destination, 
                                   Year_from = 2005,
                                   Year_till = 2018)
  Migration_1 <- Migration %>%  select(Year, Value) %>% 
    mutate_if(is.integer, as.character)
  
  # Assuylum data
  Asylum_UNHCR <- Filtering_asylum(Asylum_UNHCR_agg,
                                   origin_asylum,
                                   destination_asylum)
  Asylum <- Asylum_UNHCR %>%  select(Year, Value_asylum) %>% 
    mutate(Year = as.character(Year))
  
  
  # combine data
  Migration_GT_bind <- Migration_1 %>% 
    left_join(GT_year, by = "Year") %>% 
    left_join(Asylum, by = "Year")
  
  p <- ggplot(data=Migration_GT_bind, aes(x=Year)) +
    geom_line(aes(y=Value),color = "blue", group = 1) +
    labs(y="Migration Inflow")
  # GT data
  q <- ggplot(data=Migration_GT_bind, aes(x=Year)) +
    geom_line(aes(y = hits_average), color = "red",group = 1) +
    labs(y = "Yearly search hits")
  
  # Assuylum
  l <- ggplot(data=Migration_GT_bind, aes(x=Year)) +
    geom_line(aes(y = Value_asylum), color = "green",group = 1) +
    labs(y = "Assuylum flow")
  
  ggarrange(p, q, l,
            labels = c("Migration flow", "Search hits", "Assuylum application"),
            ncol = 1, nrow = 3)
  
}

```


# Generate function

*For Iraq to Germany with our multi specifications*

*Just Destination*
```{r}
#
Generate_comparison(serach_terms = "Germany",
                    language = 'ar',
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany",
                    origin_asylum = 'Iraq',
                    destination_asylum = 'Germany')


```
*Category and destination country*
```{r}
#with category Visa and Immigration
Generate_comparison(serach_terms = "Germany",
                    category = 555,
                    language = 'ar',
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany",
                    origin_asylum = 'Iraq',
                    destination_asylum = 'Germany')
```
*just category for origin*
```{r}
Generate_comparison(
                    category = 555,
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany",
                    origin_asylum = 'Iraq',
                    destination_asylum = 'Germany')

```


# Case 1:Forced Migration Syria
# Syria - Lebanon

*Destination*
```{r}

Generate_comparison(serach_terms = "Lebanon",
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Lebanon",
                    origin_asylum = 'Syria',
                    destination_asylum = 'Lebanon')

Filtering_migration(Migrationdata_agg,
                               "Syria",
                               "Lebanon", 
                               Year_from = 2005,
                               Year_till = 2018)

Migrationdata_agg %>% filter(Country.of.birth.nationality == "Syria", str_detect(Country,"^L"))

Asylum_UNHCR_agg %>% filter(`Country of origin` %>% str_detect("^Syrian"),str_detect(`Country of asylum`,"^J") )


Generate_comparison(serach_terms = "Jordan",
                    category = 555,
                    language = 'ar',
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Jordan",
                    origin_asylum = 'Syrian Arab Rep.',
                    destination_asylum = 'Jordan')



```
*Destination with catagory
```{r}
Generate_comparison(serach_terms = "Lebanon",
                    catagory = 555,
                    language = 'ar',
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Lebanon",
                    origin_asylum = 'Syria',
                    destination_asylum = 'Lebanon')
```

# Syria -Jordan
```{r}
Generate_comparison(serach_terms = "Jordan",
                    language = 'ar',
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Jordan",
                    origin_asylum = 'Syria',
                    destination_asylum = 'Jordan')

Generate_comparison(serach_terms = "Jordan",
                    catagory= 555,
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Jordan",
                    origin_asylum = 'Syria',
                    destination_asylum = 'Jordan')
```


# Syria -Germany
```{r}
Generate_comparison(serach_terms = "Jordan",
                    language = 'ar',
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Jordan",
                    origin_asylum = 'Syrian Arab Rep.',
                    destination_asylum = 'Jordan')

Generate_comparison(serach_terms = "Jordan",
                    catagory= 555,
                    origin_code =  "SY", 
                    origin = "Syria",
                    destination = "Jordan",
                    origin_asylum = 'Syrian Arab Rep.',
                    destination_asylum = 'Jordan')

```


# For Venezuela

# Venezuela -USA
```{r}

Generate_comparison(serach_terms = "USA",
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "United Stated of America",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'United States of America')

```

# Venezuela -Spain
*just Desintation*
```{r}

Generate_comparison(serach_terms = "Spain",
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')

```
*Destination and category*
```{r}
Generate_comparison(serach_terms = "Spain",
                    category = 555,
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')

```
*just category*
```{r}
Generate_comparison(category = 555,
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')
```


# Venezuela -Spain
*Destination*
```{r}

Generate_comparison(serach_terms = "Spain",
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')

```
*Destination and category*
```{r}
Generate_comparison(serach_terms = "Spain",
                    category = 555,
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')
```
*Just Category*
```{r}
Generate_comparison(category = 555,
                    origin_code =  "VE", 
                    origin = "Venezuela",
                    destination = "Spain",
                    origin_asylum = 'Venezuela',
                    destination_asylum = 'Spain')

```

# Other Cases  
# China to USA
```{r}

Generate_comparison(serach_terms = "USA",
                    origin_code =  "CN", 
                    origin = "China",
                    destination = "USA",
                    origin_asylum = 'China',
                    destination_asylum = 'United States of America')


```

# Mexico to USA
```{r}

Generate_comparison(serach_terms = "USA",
                    origin_code =  "MX", 
                    origin = "Mexico",
                    destination = "USA",
                    origin_asylum = 'Mexico',
                    destination_asylum = 'United States of America')


```

# India USA
```{r}

Generate_comparison(serach_terms = "USA",
                    origin_code =  "IN", 
                    origin = "India",
                    destination = "United States",
                    origin_asylum = 'India',
                    destination_asylum = 'United States')


```

# Spanish to USA
```{r}

Generate_comparison(serach_terms = "USA",
                    origin_code =  "IN", 
                    origin = "India",
                    destination = "United States",
                    origin_asylum = 'India',
                    destination_asylum = 'United States of America')


```

# Egypt to Saudi Arabia
```{r}
Generate_comparison(serach_terms = "Saudi Arabia",
                    origin_code =  "EG", 
                    origin = "Egypt",
                    destination = "Saudi Arabia",
                    origin_asylum = 'Egypt',
                    destination_asylum = 'Saudi Arabia')



```


# Morocco to Spain
*Just Destination*
```{r}
Generate_comparison(serach_terms = "Spain",
                    origin_code =  "MA", 
                    origin = "Morocco",
                    destination = "Spain",
                    origin_asylum = "Morocco",
                    destination_asylum = 'Spain')

#
```
*Destination and Category*
```{r}
Generate_comparison(serach_terms = "Spain",
                    category = 555,
                    origin_code =  "MA", 
                    origin = "Morocco",
                    destination = "Spain",
                    origin_asylum = "Morocco",
                    destination_asylum = 'Spain')

```

*Just category*
```{r}
Generate_comparison(
                    category = 555,
                    origin_code =  "MA", 
                    origin = "Morocco",
                    destination = "Spain",
                    origin_asylum = "Morocco",
                    destination_asylum = 'Spain')

```

#Algeria to France
*Just Destination*
```{r}
Generate_comparison(serach_terms = "France",
                    origin_code =  "DZ", 
                    origin = "Algeria",
                    destination = "France",
                    origin_asylum = "Algeria",
                    destination_asylum = 'France')

```

*Destination with category
```{r}
Generate_comparison(serach_terms = "France",
                    category = 555,
                    origin_code =  "DZ", 
                    origin = "Algeria",
                    destination = "France",
                    origin_asylum = "Algeria",
                    destination_asylum = 'France')

```

*Just Category*
```{r}
Generate_comparison(
                    category = 555,
                    origin_code =  "DZ", 
                    origin = "Algeria",
                    destination = "France",
                    origin_asylum = "Algeria",
                    destination_asylum = 'France')
```

#Romania - Spain
*Destintation*
```{r}
Generate_comparison( serach_terms = "Spain",
                    origin_code =  "RO", 
                    origin = "Romania",
                    destination = "Spain",
                    origin_asylum = "Romania",
                    destination_asylum = 'Spain')
```


*Destination and Category* 
```{r}
Generate_comparison( serach_terms = "Spain",
                    category = 555,
                    origin_code =  "RO", 
                    origin = "Romania",
                    destination = "Spain",
                    origin_asylum = "Romania",
                    destination_asylum = 'Spain')

```

*Just Search category*
```{r}
Generate_comparison(
                    category = 555,
                    origin_code =  "RO", 
                    origin = "Romania",
                    destination = "Spain",
                    origin_asylum = "Romania",
                    destination_asylum = 'Spain')

```
#Tunisians to Italy

*Destination*
```{r}
Generate_comparison( serach_terms = "Italy",
                    origin_code =  "TN", 
                    origin = "Tunisia",
                    destination = "Italy",
                    origin_asylum = "Tunisia",
                    destination_asylum = 'Italy')


```

*Destination and category*
```{r}
Generate_comparison( serach_terms = "Italy",
                     category = 555,
                    origin_code =  "TN", 
                    origin = "Tunisia",
                    destination = "Italy",
                    origin_asylum = "Tunisia",
                    destination_asylum = 'Italy')
```

*Just category*
```{r}
Generate_comparison(
                     category = 555,
                    origin_code =  "TN", 
                    origin = "Tunisia",
                    destination = "Italy",
                    origin_asylum = "Tunisia",
                    destination_asylum = 'Italy')
```

#comments:
1.iso code instead of country names
2.to make all graphs work when we don't have input for other graphs
3. How can we normalize flows.
4. seperate types of flows from OECD

#Ideas
1. Low scale dashboard. where policy makers can visualize on the fly
  i. 


