---
title: "Google Tends Example"
author: "Imgesu Cetin"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages('gtrendsR')
library(gtrendsR)

```

#rudimentary descriptive statistics
```{r}
#Whether the 2015 “refugee crisis” increased search behaviors
 
#Google Trends for 'migration' for Syria, Afganistan, Iraq. 

data("countries")

#change of google trends hit for keyword "migration"
res<-gtrends('migration',geo=c("SY","AF","IQ"))
plot(res)

```
#comment: I assume that the countries that do not use english as search words have close to 0 during some times.This may mean we should be searching for Arabic key words. Perhaps use google translate.


```{r}
#keyword searches for migration,immigration,asylum for Syria

res<-gtrends(c("migration","immigration","asylum"),geo="SY")
plot(res)

#this looks quite noisy.
```


```{r}
#google searches for Afganistan


#unique(countries)
#unique(countries$country_code)
res<-gtrends("migration",geo="AF")

plot(res)
```
```{r}
#google searches for H1 for Syria



res<-gtrends(c("H1","flight"),geo="SY")

plot(res)

#something interesting is that search intensity drops down to 0 during some times durinig the years...
```

```{r}
#preview of the data: to see how it is stores.(year-month-day) 
res
```

#some interesting notes
#when using google trends API we can see hits according to region. For example Damascus Governorate had the most of the searches for H1 visa. 



```{r}
#using reshape to reshape data
library(reshape2)

#getting gtrends hits for the keyword visa for Germany,France,Italy,Spain. for all times (20)

google.trends.visa <- gtrends(c("visa"),geo = c("DE","FR","IT","ES"), time = "all")

plot(google.trends.visa)

google.trends = dcast(google.trends.visa, date ~ keyword + geo, value.var = "hits")

#looks as though the data for European countries are more stable, not many 0's. I assume the countries where English is not prominently used have more lower hits of english migration key words. Prehaps we can use Arabic to see if this changes. 
```


```{r}
#looking at the data
google.trends.visa <- gtrends(c("visa"),geo = c("DE","FR","IT","ES"), time = "today+5-y")

head(google.trends.visa)
```

#visualize migration keyword for the countries
```{r}
google.trends.migration <- gtrends(c("migration"),geo = c("DE","FR","IT","ES"), time = "all")

plot(google.trends.migration)
```

Migration data
#Data cleaning
```{r}
#loading data for data cleaning
migrationData <- read_csv("~/Documents/projects/UN-Project/Google Trends Project/migrationData.csv")

migrationData

#I think we should have variables for inflow migration, outflow migration.Needs data cleaning. How should we structure the data that is best for our forecasting?
```
```{r}

```

