---
title: "Google Tends Example"
author: "Murtiza"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
#install.packages('gtrendsR')
library(gtrendsR)
library("dplyr")
library("stringr")
library(ggplot2)
library("tidyverse")
library(ggpubr)

```

# Lets try with catogory

```{r}
#for origin country Iraq, when keyword is Turkey for the catagory of Visa and Immigration and when language is Arabic.

res<-gtrends('turkey',geo=c("IQ"),time='all',category = 555,hl='ar')
plot(res)

#some kind of influence of trends for migration? There is a spike after 2013?
```

```{r}
GT_DE <- gtrends(c("migration to Germany"),geo = "DE", time = "now 7-d",
                 onlyInterest = TRUE)
head(GT_DE)

Cat <- force(categories)
Cat_interest <- Cat %>% filter(Cat$name %>% str_detect("migration"))

GT_DE <- gtrends(geo = "DE", time = "today+5-y",
                 onlyInterest = TRUE, category = 1313)
GT_DE_dutch <- gtrends(geo = "DE", time = "today+5-y",
                 onlyInterest = TRUE, category = 1313, hl = "de")
data("hl")
```

Methodology
```{r}
# our methodology for the time being
GT_IQ_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
plot(GT_IQ_GE_01)

# Bilateral
GT_IQ_GE_02<-gtrends(c("visa Germany","work Germany", "migrant Germany"),geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02)

#Univariate
GT_IQ_GE_03<-gtrends("Migration",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

# Destination
GT_IQ_GE_04 <-gtrends("Germany",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

```

Here we are taking the average of the yearly search hits
Iraq VS Germany, Category = "Visa & Immigration"
```{r}
GT_IQ_GE_eg<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```
Iraq VS Germany, Category = "Immigration Policy & Border Issues"
```{r}
GT_IQ_GE_eg_2<-gtrends('Germany',geo=c("IQ"),time='2004-01-01 2018-01-01',category = 1313,hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year_2 <- GT_IQ_GE_eg_2 %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         1313),][[1]][1])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year_2, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()
```

I also tried with different countries, it seems the data is far from the found truth. Our new methodology might not work or need to be optimized.

Lets try with other scenarios.
("visa Germany","work Germany", "migrant Germany")

```{r}
# Bilateral
GT_IQ_GE_02_year <- GT_IQ_GE_02[[1]] %>% group_by(date, geo) %>% summarise(hits_average = sum(hits)) %>% ungroup() %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% group_by(Year, geo) %>% summarise(hits_average = mean(hits_average))
  
ggplot(data=GT_IQ_GE_02_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```
Univarriate with origin country
"Migration"
```{r}
# Here I found some non-numeric values (typos in the data), so I cleaned
GT_IQ_GE_03[[1]] %>%  filter(str_detect(date,"^2013")) 
# Univarriate
GT_IQ_GE_03_year <- GT_IQ_GE_03[[1]]  %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% 
  mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
  group_by(Year, keyword,geo) %>% 
  summarise(hits_average = mean(as.numeric(hits)))


ggplot(data=GT_IQ_GE_03_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```

Destination 
"Germany"

```{r}
# Here I found some non-numeric values (typos in the data), so I cleaned
GT_IQ_GE_04[[1]] %>%  filter(str_detect(date,"^2013")) 
# Univarriate
GT_IQ_GE_04_year <- GT_IQ_GE_04[[1]]  %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% 
  mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
  group_by(Year, keyword,geo) %>% 
  summarise(hits_average = mean(as.numeric(hits)))


ggplot(data=GT_IQ_GE_04_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()


```
Simple prediciton
```{r}
library("tseries")
library("forecast")
tsdata <- GT_IQ_GE_04_year %>% ungroup() %>% 
  select(hits_average) %>% 
  ts(start = 2004)

fit <- auto.arima(tsdata,
                            trace=T, 
                            stepwise = T,
                            stationary=T,
                            approximation=FALSE,
                            seasonal = F,
                            lambda = 0)

checkresiduals(fit)
arima_forcast100 <- forecast::forecast(fit, h = 13, lambda = 0, biasadj = TRUE)
autoplot(tsdata) + autolayer(arima_forcast100)
```

Comparison with Migration trends

Data preparing
<<<<<<< HEAD
```{r}
s
=======
```{r message=FALSE}
Migrationdata <- read.csv("migrationData.csv")
>>>>>>> 1e3c14e508e463a699418398de0f581a2e79eb5a
source("Functions.R")


Migrationdata_agg <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))

# Assuylum Data from UNHCR
asylum_applications_UNHCR<-read_csv("asylum-applications_data.csv")


Asylum_UNHCR_agg<-asylum_applications_UNHCR%>%
  group_by(`Country of origin`,`Country of asylum`,Year) %>%
  summarise(Value_asylum=sum(applied))

```


Category--- SY-Ge
```{r warning=F, message=F}
# 
# # GT data
# GT_SY_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
# GT_SY_GE_year_1 <- Agg_yearly(GT_SY_GE_01) %>%  
#   filter(Year >2005, Year < 2018) %>% ungroup() %>% 
#   select(Year, hits_average)
# 
# 
# # Migration data
# Sy_GE <- Filtering_migration(Migrationdata_agg,
#                              origin = "Syria",
#                              destination = "Germany",
#                              Year_from = 2005,
#                              Year_till = 2018)
# Sy_GE_1 <- Sy_GE %>%  select(Year, Value) %>% 
#   mutate_if(is.integer, as.character)
# 
# # combine data
# Syria_Germany_bind <- Sy_GE_1 %>% 
#   left_join(GT_SY_GE_year_1, by = "Year")
# # plot
# # ggplot(data=Syria_Germany_bind, aes(x=Year)) +
# #   geom_line(aes(y=log(Value),color = "Migration_log"), group = 1) +
# #   geom_line(aes(y = hits_average, color = "GT_search_hits"),group = 1)
# # Migration data
# p <- ggplot(data=Syria_Germany_bind, aes(x=Year)) +
#   geom_line(aes(y=Value),color = "blue", group = 1) +
#   labs(y="Migration Inflow")
# # GT data
# q <- ggplot(data=Syria_Germany_bind, aes(x=Year)) +
#   geom_line(aes(y = hits_average), color = "red",group = 1) +
#   labs(y = "Yearly search hits")
# 
# ggarrange(p, q, 
#           labels = c("Migration flow", "Search hits"),
#           ncol = 1, nrow = 2)

```


```{r message=FALSE}
# Syria-> Germany
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Germany")
# Destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Germany")


# Syria-> Turkey
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Turkey")
# Destination
Generate_comparison(serach_terms = "Turkey", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Turkey")

# Iraq-> Germany
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")
# Destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")

# Iraq-> Turkey
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Turkey")
# Destination
<<<<<<< HEAD
Generate_comparison(serach_terms = "Germany",
                    category=555,
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany")
=======
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ", 
                    category = 555,
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")

>>>>>>> 1e3c14e508e463a699418398de0f581a2e79eb5a


library(ggpubr)
```
So with and without keyword with/without category
```{r message=FALSE}
# Category
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY",
                    category = 555,
                    origin = "Syria",
                    destination = "Germany")
# destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY",
                    origin = "Syria",
                    destination = "Germany")

# Category without key word
Generate_comparison(category = 555, 
                    origin_code =  "SY",
                    origin = "Syria",
                    destination = "Germany")

### Iraq

# Category
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ",
                    category = 555,
                    origin = "Iraq",
                    destination = "Germany")
# destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ",
                    origin = "Iraq",
                    destination = "Germany")

# Category without key word
Generate_comparison(category = 555, 
                    origin_code =  "IQ",
                    origin = "Iraq",
                    destination = "Germany")


```
```{r}


Generate_comparison(serach_terms = "Germany",
                    language = 'ar',
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany",
                    origin_asylum = 'Iraq',
                    destination_asylum = 'Germany')

```




Similarity check btw Migration flow and GT data
```{r}
# 1. Similarity: I decided to use L1 norm since it is robust to outliers.
# 2. Normalization: Since GT data scale is fro 0-100, I normalize the data into scale from 0 to 1 and multiply 100, so we can compare the trend.
# So the function is updated accordingly and added relative plots and arguments.

```

```{r}
# Data 
Migrationdata <- read.csv("migrationData.csv")
source("Functions.R")

# total migration OECD
Migrationdata_agg <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))
# Asylum OEDC
Asylum_OEDC <-  Migrationdata %>% 
  filter(str_detect(Variable, "^Inflows of asylum")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))

# Assuylum Data from UNHCR
asylum_applications_UNHCR<-read_csv("asylum-applications_data.csv")


Asylum_UNHCR_agg<-asylum_applications_UNHCR%>%
  group_by(`Country of origin`,`Country of asylum`,Year) %>%
  summarise(Value_asylum=sum(applied))



# try the new function
# GT data
# 1. Category
GT_SY_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_1 <- Agg_yearly(GT_SY_GE_01) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_1_hits = hits_average)
# 2. Destination
GT_SY_GE_02<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_2 <- Agg_yearly(GT_SY_GE_02) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_2_hits = hits_average)

# 3. without any search term with the category
GT_SY_GE_03<-gtrends(geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_3 <- Agg_yearly(GT_SY_GE_03) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_3_hits = hits_average)

# normalize to scale 0-100
normalized <- function(x){
  ((x-min(x))/(max(x)-min(x)))*100
}

# Lets try a single example of Syria to Germany
# 1. Migration total
Sy_GE_total <- Filtering_migration(Migrationdata_agg,
                             origin = "Syria",
                             destination = "Germany",
                             Year_from = 2005,
                             Year_till = 2018)
Sy_GE_total_1 <- Sy_GE_total %>%  select(Year, Value) %>%
  mutate_if(is.integer, as.character) %>% 
  mutate(migration_flow_total = normalized(Value)) %>% 
  select(-Value)

# 2. Asylum OEDC
Sy_GE_asylum_OEDC <- Filtering_migration(Asylum_OEDC,
                             origin = "Syria",
                             destination = "Germany",
                             Year_from = 2005,
                             Year_till = 2018)
Sy_GE_asylum_OEDC_1 <- Sy_GE_asylum_OEDC %>%  ungroup() %>% 
  select(Year, Value) %>%
  mutate_if(is.integer, as.character) %>% 
  mutate(Asylum_OEDC = normalized(Value)) %>% 
  select(-Value)

# 3. Asylum UNHCR
Sy_GE_asylum_UNHCR <- Filtering_asylum(Asylum_UNHCR_agg,
                             "Syrian Arab Rep.",
                             "Germany")
Sy_GE_asylum_UNHCR_1 <- Sy_GE_asylum_UNHCR %>% ungroup() %>% 
  select(Year, Value_asylum) %>%
  mutate(Year = as.character(Year),
         Asylum_UNHCR = normalized(Value_asylum)) %>% 
  select(-Value_asylum)
  
# merge the data
Migration_GT_merge <- Sy_GE_total_1 %>% 
    left_join(Sy_GE_asylum_OEDC_1, by = "Year") %>% 
    left_join(Sy_GE_asylum_UNHCR_1, by = "Year") %>%
    left_join(GT_SY_GE_year_1, by = "Year") %>% 
    left_join(GT_SY_GE_year_2, by = "Year")%>% 
    left_join(GT_SY_GE_year_3, by = "Year")

# Asylum_UNHCR_agg %>% filter(`Country of origin` %>% str_detect("^Syrian"),str_detect(`Country of asylum`,"^G") )

Scale_x <- scale_x_continuous(breaks = waiver(), n.breaks = 7)
# Migration total
A <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=migration_flow_total),color = "blue", group = 1) + labs(title ="Migration Inflow", y = "", x= "") + 
  ylim(0,100) + Scale_x

# Asylum OEDC
B <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Asylum_OEDC),color = "red", group = 1) +
  labs(title ="Asylum OECD", y = "",x= "") + ylim(0,100)+ Scale_x
# Asylum UNHCR
C <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Asylum_UNHCR),color = "red", group = 1) +
  labs(title ="Asylum UNHCR", y = "",x= "") + 
  ylim(0,100) + xlim(2014,2017)



# annotate("text", x=8, y=13000, label= "boat")
# Approach 1
p <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Approach_1_hits),color = "Green", group = 1) +
   ylim(0,100) 
# Approach 2
q <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y = Approach_2_hits), color = "black",group = 1) +
  labs(y = "A2", x= "") + ylim(0,100)
# Approach 3
d <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y = Approach_3_hits), color = "navy",group = 1) +
  labs(y = "A3", x= "") + ylim(0,100)

# My_Theme = theme(
#   axis.title.x = element_text(size = 10),
#   axis.text.x = element_text(size = 10),
#   axis.title.y = element_text(size = 10))

ggarrange(A,B,C,
          p +labs(y="A1", x= "")+ Scale_x,
          p +labs(y="", x= "")+ Scale_x,
          p + labs(y="", x= "") + xlim(2014,2017),
          q +labs(y="A2", x= "")+ Scale_x,
          q +labs(y="", x= "")+ Scale_x,
          q + labs(y="", x= "") + xlim(2014,2017),
          d +labs(y="A3", x= "")+ Scale_x,
          d +labs(y="", x= "")+ Scale_x,
          d + labs(y="", x= "") + xlim(2014,2017),
          heights = c(2, 2),
          ncol = 3, nrow = 4)

# Similarity
# similarity_1 <- 
# 
# library("ggrepel")
# library(PET)
# install.packages("PET")

```

```{r}
# Data 
Migrationdata <- read.csv("migrationData.csv")
source("Functions.R")

# total migration OECD
Migrationdata_agg <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))
# Asylum OEDC
Asylum_OEDC <-  Migrationdata %>% 
  filter(str_detect(Variable, "^Inflows of asylum")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))

# Assuylum Data from UNHCR
asylum_applications_UNHCR<-read_csv("asylum-applications_data.csv")


Asylum_UNHCR_agg<-asylum_applications_UNHCR%>%
  group_by(`Country of origin`,`Country of asylum`,Year) %>%
  summarise(Value_asylum=sum(applied))



# try the new function
# GT data
# 1. Category
GT_SY_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_1 <- Agg_yearly(GT_SY_GE_01) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_1_hits = hits_average)
# 2. Destination
GT_SY_GE_02<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_2 <- Agg_yearly(GT_SY_GE_02) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_2_hits = hits_average)

# 3. without any search term with the category
GT_SY_GE_03<-gtrends(geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_3 <- Agg_yearly(GT_SY_GE_03) %>%
  filter(Year >2005, Year < 2018) %>% ungroup() %>%
  select(Year, hits_average) %>% 
  rename(Approach_3_hits = hits_average)

# normalize to scale 0-100
normalized <- function(x){
  ((x-min(x))/(max(x)-min(x)))*100
}

# Lets try a single example of Syria to Germany
# 1. Migration total
Sy_GE_total <- Filtering_migration(Migrationdata_agg,
                             origin = "Syria",
                             destination = "Germany",
                             Year_from = 2005,
                             Year_till = 2018)
Sy_GE_total_1 <- Sy_GE_total %>%  select(Year, Value) %>%
  mutate_if(is.integer, as.character) %>% 
  mutate(migration_flow_total = normalized(Value)) %>% 
  select(-Value)

# 2. Asylum OEDC
Sy_GE_asylum_OEDC <- Filtering_migration(Asylum_OEDC,
                             origin = "Syria",
                             destination = "Germany",
                             Year_from = 2005,
                             Year_till = 2018)
Sy_GE_asylum_OEDC_1 <- Sy_GE_asylum_OEDC %>%  ungroup() %>% 
  select(Year, Value) %>%
  mutate_if(is.integer, as.character) %>% 
  mutate(Asylum_OEDC = normalized(Value)) %>% 
  select(-Value)

# 3. Asylum UNHCR
Sy_GE_asylum_UNHCR <- Filtering_asylum(Asylum_UNHCR_agg,
                             "Syrian Arab Rep.",
                             "Germany")
Sy_GE_asylum_UNHCR_1 <- Sy_GE_asylum_UNHCR %>% ungroup() %>% 
  select(Year, Value_asylum) %>%
  mutate(Year = as.character(Year),
         Asylum_UNHCR = normalized(Value_asylum)) %>% 
  select(-Value_asylum)
  
# merge the data
Migration_GT_merge <- Sy_GE_total_1 %>% 
    left_join(Sy_GE_asylum_OEDC_1, by = "Year") %>% 
    left_join(Sy_GE_asylum_UNHCR_1, by = "Year") %>%
    left_join(GT_SY_GE_year_1, by = "Year") %>% 
    left_join(GT_SY_GE_year_2, by = "Year")%>% 
    left_join(GT_SY_GE_year_3, by = "Year")

# Asylum_UNHCR_agg %>% filter(`Country of origin` %>% str_detect("^Syrian"),str_detect(`Country of asylum`,"^G") )

Scale_x <- scale_x_continuous(breaks = waiver(), n.breaks = 7)
# Migration total
A <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=migration_flow_total),color = "blue", group = 1) + labs(title ="Migration Inflow", y = "", x= "") + 
  ylim(0,100) + Scale_x

# Asylum OEDC
B <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Asylum_OEDC),color = "red", group = 1) +
  labs(title ="Asylum OECD", y = "",x= "") + ylim(0,100)+ Scale_x
# Asylum UNHCR
C <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Asylum_UNHCR),color = "red", group = 1) +
  labs(title ="Asylum UNHCR", y = "",x= "") + 
  ylim(0,100) + xlim(2014,2017)



# annotate("text", x=8, y=13000, label= "boat")
# Approach 1
p <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y=Approach_1_hits),color = "Green", group = 1) +
   ylim(0,100) 
# Approach 2
q <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y = Approach_2_hits), color = "black",group = 1) +
  labs(y = "A2", x= "") + ylim(0,100)
# Approach 3
d <- ggplot(data=Migration_GT_merge, aes(x=as.integer(Year))) +
  geom_line(aes(y = Approach_3_hits), color = "navy",group = 1) +
  labs(y = "A3", x= "") + ylim(0,100)

# My_Theme = theme(
#   axis.title.x = element_text(size = 10),
#   axis.text.x = element_text(size = 10),
#   axis.title.y = element_text(size = 10))

ggarrange(A,B,C,
          p +labs(y="A1", x= "")+ Scale_x,
          p +labs(y="", x= "")+ Scale_x,
          p + labs(y="", x= "") + xlim(2014,2017),
          q +labs(y="A2", x= "")+ Scale_x,
          q +labs(y="", x= "")+ Scale_x,
          q + labs(y="", x= "") + xlim(2014,2017),
          d +labs(y="A3", x= "")+ Scale_x,
          d +labs(y="", x= "")+ Scale_x,
          d + labs(y="", x= "") + xlim(2014,2017),
          heights = c(2, 2),
          ncol = 3, nrow = 4)



```



