---
title: "Google Tends Example"
author: "Murtiza"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
#install.packages('gtrendsR')
library(gtrendsR)
library("dplyr")
library("stringr")
library(ggplot2)
library("tidyverse")
library(ggpubr)

```

# Lets try with catogory

```{r}
#for origin country Iraq, when keyword is Turkey for the catagory of Visa and Immigration and when language is Arabic.

res<-gtrends('turkey',geo=c("IQ"),time='all',category = 555,hl='ar')
plot(res)

#some kind of influence of trends for migration? There is a spike after 2013?
```

```{r}
GT_DE <- gtrends(c("migration to Germany"),geo = "DE", time = "now 7-d",
                 onlyInterest = TRUE)
head(GT_DE)

Cat <- force(categories)
Cat_interest <- Cat %>% filter(Cat$name %>% str_detect("migration"))

GT_DE <- gtrends(geo = "DE", time = "today+5-y",
                 onlyInterest = TRUE, category = 1313)
GT_DE_dutch <- gtrends(geo = "DE", time = "today+5-y",
                 onlyInterest = TRUE, category = 1313, hl = "de")
data("hl")
```

Methodology
```{r}
# our methodology for the time being
GT_IQ_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
plot(GT_IQ_GE_01)

# Bilateral
GT_IQ_GE_02<-gtrends(c("visa Germany","work Germany", "migrant Germany"),geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02)

#Univariate
GT_IQ_GE_03<-gtrends("Migration",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

# Destination
GT_IQ_GE_04 <-gtrends("Germany",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

```

Here we are taking the average of the yearly search hits
Iraq VS Germany, Category = "Visa & Immigration"
```{r}
GT_IQ_GE_eg<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```
Iraq VS Germany, Category = "Immigration Policy & Border Issues"
```{r}
GT_IQ_GE_eg_2<-gtrends('Germany',geo=c("IQ"),time='2004-01-01 2018-01-01',category = 1313,hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year_2 <- GT_IQ_GE_eg_2 %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         1313),][[1]][1])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year_2, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()
```

I also tried with different countries, it seems the data is far from the found truth. Our new methodology might not work or need to be optimized.

Lets try with other scenarios.
("visa Germany","work Germany", "migrant Germany")

```{r}
# Bilateral
GT_IQ_GE_02_year <- GT_IQ_GE_02[[1]] %>% group_by(date, geo) %>% summarise(hits_average = sum(hits)) %>% ungroup() %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% group_by(Year, geo) %>% summarise(hits_average = mean(hits_average))
  
ggplot(data=GT_IQ_GE_02_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```
Univarriate with origin country
"Migration"
```{r}
# Here I found some non-numeric values (typos in the data), so I cleaned
GT_IQ_GE_03[[1]] %>%  filter(str_detect(date,"^2013")) 
# Univarriate
GT_IQ_GE_03_year <- GT_IQ_GE_03[[1]]  %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% 
  mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
  group_by(Year, keyword,geo) %>% 
  summarise(hits_average = mean(as.numeric(hits)))


ggplot(data=GT_IQ_GE_03_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```

Destination 
"Germany"

```{r}
# Here I found some non-numeric values (typos in the data), so I cleaned
GT_IQ_GE_04[[1]] %>%  filter(str_detect(date,"^2013")) 
# Univarriate
GT_IQ_GE_04_year <- GT_IQ_GE_04[[1]]  %>% 
  mutate(Year =str_extract(date, "^.{4}")) %>% 
  mutate(hits = gsub("[^0-9.-]", "", hits)) %>% 
  group_by(Year, keyword,geo) %>% 
  summarise(hits_average = mean(as.numeric(hits)))


ggplot(data=GT_IQ_GE_04_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()


```
Simple prediciton
```{r}
library("tseries")
library("forecast")
tsdata <- GT_IQ_GE_04_year %>% ungroup() %>% 
  select(hits_average) %>% 
  ts(start = 2004)

fit <- auto.arima(tsdata,
                            trace=T, 
                            stepwise = T,
                            stationary=T,
                            approximation=FALSE,
                            seasonal = F,
                            lambda = 0)

checkresiduals(fit)
arima_forcast100 <- forecast::forecast(fit, h = 13, lambda = 0, biasadj = TRUE)
autoplot(tsdata) + autolayer(arima_forcast100)
```

Comparison with Migration trends

Data preparing
```{r}
Migrationdata <- read.csv("migrationData.csv")
source("Functions.R")


Migrationdata %>% filter(str_detect(Variable, "^Inflows")) %>%
  distinct(VAR)
Migrationdata %>%  filter(VAR == "B13")

Migrationdata_agg <- Migrationdata %>%  
  filter(str_detect(Variable, "^Inflows")) %>% 
  group_by(Country.of.birth.nationality, Country, Year) %>% 
  summarise(Value = sum(Value))

```


Category--- SY-Ge
```{r warning=F, message=F}

# GT data
GT_SY_GE_01<-gtrends('Germany',geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
GT_SY_GE_year_1 <- Agg_yearly(GT_SY_GE_01) %>%  
  filter(Year >2005, Year < 2018) %>% ungroup() %>% 
  select(Year, hits_average)


# Migration data
Sy_GE <- Filtering_migration(Migrationdata_agg,
                             origin = "Syria",
                             destination = "Germany",
                             Year_from = 2005,
                             Year_till = 2018)
Sy_GE_1 <- Sy_GE %>%  select(Year, Value) %>% 
  mutate_if(is.integer, as.character)

# combine data
Syria_Germany_bind <- Sy_GE_1 %>% 
  left_join(GT_SY_GE_year_1, by = "Year")
# plot
# ggplot(data=Syria_Germany_bind, aes(x=Year)) +
#   geom_line(aes(y=log(Value),color = "Migration_log"), group = 1) +
#   geom_line(aes(y = hits_average, color = "GT_search_hits"),group = 1)
# Migration data
p <- ggplot(data=Syria_Germany_bind, aes(x=Year)) +
  geom_line(aes(y=Value),color = "blue", group = 1) +
  labs(y="Migration Inflow")
# GT data
q <- ggplot(data=Syria_Germany_bind, aes(x=Year)) +
  geom_line(aes(y = hits_average), color = "red",group = 1) +
  labs(y = "Yearly search hits")

ggarrange(p, q, 
          labels = c("Migration flow", "Search hits"),
          ncol = 1, nrow = 2)

```


```{r message=FALSE}
# Syria-> Germany
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Germany")
# Destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Germany")


# Syria-> Turkey
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Turkey")
# Destination
Generate_comparison(serach_terms = "Turkey", 
                    origin_code =  "SY", 
                    language = "ar", 
                    origin = "Syria",
                    destination = "Turkey")

# Iraq-> Germany
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")
# Destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")

# Iraq-> Turkey
# univariate
Generate_comparison(serach_terms = "Migration", 
                    origin_code =  "IQ", 
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Turkey")
# Destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ", 
                    category = 555,
                    language = "ar", 
                    origin = "Iraq",
                    destination = "Germany")



```
So with and without keyword with/without category
```{r message=FALSE}
# Category
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY",
                    category = 555,
                    origin = "Syria",
                    destination = "Germany")
# destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "SY",
                    origin = "Syria",
                    destination = "Germany")

# Category without key word
Generate_comparison(category = 555, 
                    origin_code =  "SY",
                    origin = "Syria",
                    destination = "Germany")

### Iraq

# Category
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ",
                    category = 555,
                    origin = "Iraq",
                    destination = "Germany")
# destination
Generate_comparison(serach_terms = "Germany", 
                    origin_code =  "IQ",
                    origin = "Iraq",
                    destination = "Germany")

# Category without key word
Generate_comparison(category = 555, 
                    origin_code =  "IQ",
                    origin = "Iraq",
                    destination = "Germany")


```
```{r}
# Assuylum Data from UNHCR
asylum_applications_UNHCR<-read_csv("asylum-applications_data.csv")


Asylum_UNHCR_agg<-asylum_applications_UNHCR%>%
  group_by(`Country of origin`,`Country of asylum`,Year) %>%
  summarise(Value_asylum=sum(applied))
# Assuylum
A <- Filtering_asylum(Asylum_UNHCR_agg,
                             "Afghanistan",
                             "Australia")

A <- A %>% select(Year, Value_asylum) %>% 
    mutate(Year = as.character(Year))

str(A$Year)
# Migration
B <- Filtering_migration(Migrationdata_agg,
                               "Afghanistan",
                               "Australia", 
                               Year_from = 2005,
                               Year_till = 2018) %>% 
  select(Year, Value) %>% 
    mutate_if(is.integer, as.character)
  


str(B$Year)
# GT
GT<-gtrends(keyword = "Australia",geo=c("SY"), 
                       time='2004-01-01 2017-12-31',
                       gprop = "web", onlyInterest = TRUE)
  
GT_year <- Agg_yearly(GT)  %>%
    ungroup() %>% 
    select(Year, hits_average)
  
  
Migration_GT_bind <- B %>% 
    left_join(GT_year, by = "Year") %>% 
    left_join(A, by = "Year")

Generate_comparison(serach_terms = "Germany",
                    language = 'ar',
                    origin_code =  "IQ", 
                    origin = "Iraq",
                    destination = "Germany",
                    origin_asylum = 'Iraq',
                    destination_asylum = 'Germany')

```





```{r}

# our methodology for the time being
GT_IQ_GE_01<-gtrends(keyword = NA,geo=c("SY"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
plot(GT_IQ_GE_01)

# Bilateral
GT_IQ_GE_02<-gtrends(c("visa Germany","work Germany", "migrant Germany"),geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02)

#Univariate
GT_IQ_GE_03<-gtrends("Migration",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

# Destination
GT_IQ_GE_04 <-gtrends("Germany",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)



```

