---
title: "Methodology Testing"
author: "Imgesu Cetin"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#set up work envirornment
library(gtrendsR)
library("dplyr")
library("stringr")
library(ggplot2)
library(readr)
#install.packages('googletrends')



data('countries')


migrationData <- read_csv("migrationData copy.csv")
migrationData
```

```{r}
#setting up catagories
Cat <- force(categories)
Cat_interest <- Cat %>% filter(Cat$name %>% str_detect("migration"))
```

# Methodology for Iraq to Germany
```{r}
library(reshape2)
# our methodology for the time being
GT_IQ_GE_01<-gtrends('Germany',geo=c("IQ"),time='2004-01-01 2018-12-31',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)
plot(GT_IQ_GE_01)

# Bilateral
GT_IQ_GE_02<-gtrends(c("visa Germany","work Germany", "migrant Germany"),geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02)


#aggregate all searches next to each other
google.trends = dcast(GT_IQ_GE_02$interest_over_time, date ~ unique(keyword) + geo, value.var = "hits")
rownames(google.trends) = google.trends$date
#preview data
head(google.trends)
#we may now simple take the aggregated 3 columns of 'visa Germany', 'work germany' all as colums. 
#we may even want to expand by taking more words that may be relevant and adding to the merged data


#Bilateral individual cases
GT_IQ_GE_02.1<-gtrends("visa Germany", geo=c("IQ"),time='2004-01-01 2018-01-01', hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02.1)

GT_IQ_GE_02.2<-gtrends("migrant Germany", geo=c("IQ"),time='2004-01-01 2018-01-01', hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_02.2)

#Univariate
GT_IQ_GE_03<-gtrends("Migration",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)
plot(GT_IQ_GE_03)

# Destination
GT_IQ_GE_04 <-gtrends("Germany",geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar', onlyInterest = TRUE)

```

# Trying with our proposed Methodology, with catagory=555

#no results...
```{r}
GT_IQ_GE_eg<-gtrends('Germany',geo=c("IQ"),time='2004-01-01 2018-01-01',category = 555,hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

#No results with Iraq when query is 'germany'
```

# Bivariate case
```{r}
GT_IQ_GE_eg<-gtrends('visa Germany',geo=c("IQ"),time='2004-01-01 2018-01-01',hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```

# Comparing to historic Migration data to the bivariate case of 'visa germany'

```{r}
#filter through migration data for Iraq to Germany for years 2004-2018
Iraq_Germany <- migrationData %>%  
  filter(str_detect(Variable, "^Inflows"))%>% 
  filter(CO2 == "IRQ", Country == "Germany", VAR == "B11")%>%
  filter(Year > 2003)


GT_IQ_GE_year_bivar <- GT_IQ_GE_year %>%  filter(Year != 2018) %>% 
  ungroup() %>% 
  select(Year, hits_average)

Iraq_Germany_1 <- Iraq_Germany %>%select(Year, Value)
Iraq_Germany_bind <- merge(Iraq_Germany_1, GT_IQ_GE_year_1, by = "Year")


ggplot(data=Iraq_Germany_bind, aes(x=Year, y=Value)) +
  geom_line(color = "red")+
  geom_line(aes(x=Year, y = 3000*hits_average), color = "blue")

#looks as though it does not capture actual migration data in the bivariate case for keyword 'visa germany'
```

# Bivariate case continued with both bivariate, univariate, and destination. Aggregation of all bivariate search terms into one variable.

```{r}
# adding search terms

GT_IQ_GE_agg<-gtrends(c('visa Germany','work Germany','job Germany','germany','immigrate'),geo=c("IQ"),time='2005-01-01 2018-01-01',hl='ar',gprop = "web", onlyInterest = TRUE)
#aggregate all searches next to each other
google.trends = dcast(GT_IQ_GE_agg$interest_over_time, date ~ unique(keyword) + geo, value.var = "hits")
rownames(google.trends) = google.trends$date
#preview data
google.trends

#reshape data to take aggreagate according to date

google.trends %>%
  group_by(date) %>%
  summarise(Tot.migrate = sum(google.trends[1:5]))


GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


```


# univariate case 'migration' for Iraq


```{r}
data('hl')
#Univariate
IQ_GE_uni_ar<-gtrends("الهجرة",geo=c("IQ"),time='2004-01-01 2018-01-01', onlyInterest = TRUE)
plot(IQ_GE_uni_ar)

IQ_GE_uni_en<-gtrends("immigration",geo=c("IQ"),hl='ar',time='2004-01-01 2018-01-01', onlyInterest = TRUE)
plot(IQ_GE_uni_en)

#there is a difference between when we use arabic characters and when we use latin characters and use the language ht='ar'. I'm not sure how we can overcome this.
```

# I  believe that we should take our 2004 results. 
```{r}
library(stringr)

#filter through migration data for Iraq to Germany for years 2006-2018
Iraq_Germany_2006.2018 <- migrationData %>%  
  filter(str_detect(Variable, "^Inflows"))%>% 
  filter(CO2 == "IRQ", Country == "Germany", VAR == "B11")%>%
  filter(Year > 2003)

IQ_GE_year <- IQ_GE_uni_ar$interest_over_time %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),])


# Basic line plot with points
ggplot(data=IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

IQ_GE_year

```
#lets compare with actual historic data

```{r}
IQ_GE_year_1 <- IQ_GE_year %>%  filter(Year != 2018) %>% 
  ungroup() %>% 
  select(Year, hits_average)



Iraq_Germany_1 <- Iraq_Germany_2006.2018 %>%select(Year, Value)
Iraq_Germany_bind <- merge(Iraq_Germany_1, IQ_GE_year_1, by = "Year")


ggplot(data=Iraq_Germany_bind, aes(x=Year, y=Value)) +
  geom_line(color = "red")+
  geom_line(aes(x=Year, y = 2000*hits_average), color = "blue")

```


# Destination case 'Germany' for Iraq with category
```{r}
GT_IQ_GE_eg<-gtrends('Germany',geo=c("IQ"),time='2005-01-01 2018-01-01', hl='ar',category=555,gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()

```
#just destination without category
```{r}
GT_IQ_GE_eg<-gtrends('Germany',geo=c("IQ"),time='2005-01-01 2018-01-01', hl='ar',gprop = "web", onlyInterest = TRUE)[[1]]
GT_IQ_GE_year <- GT_IQ_GE_eg %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])


# Basic line plot with points
ggplot(data=GT_IQ_GE_year, aes(x=Year, y=hits_average, group=1)) +
  geom_line()+
  geom_point()
```

#comparing with historic migration data

```{r}
#filter through migration data for Iraq to Germany for years 2004-2018
Iraq_Germany <- migrationData %>%  
  filter(str_detect(Variable, "^Inflows"))%>% 
  filter(CO2 == "IRQ", Country == "Germany", VAR == "B11")%>%
  filter(Year > 2004)


GT_IQ_GE_year_1 <- GT_IQ_GE_year %>%  filter(Year != 2018) %>% 
  ungroup() %>% 
  select(Year, hits_average)

Iraq_Germany_1 <- Iraq_Germany %>%select(Year, Value)
Iraq_Germany_bind <- merge(Iraq_Germany_1, GT_IQ_GE_year_1, by = "Year")


ggplot(data=Iraq_Germany_bind, aes(x=Year, y=Value)) +
  geom_line(color = "red")+
  geom_line(aes(x=Year, y = 2000*hits_average), color = "blue")

```

#aggregate of all cases into one catagory.

```{r}
#adding destination,bivariate case
IQ_GE_uni_en<-gtrends("immigration",geo=c("IQ"),hl='ar',time='2005-01-01 2018-01-01', onlyInterest = TRUE)[[1]]
IQ_GE_uni_en <- IQ_GE_uni_en %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])

IQ_GE_des<-gtrends("Germany",geo=c("IQ"),hl='ar',time='2005-01-01 2018-01-01', onlyInterest = TRUE)
IQ_GE_des <- IQ_GE_des%>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),]
IQ_GE_des

IQ_GE_biv.1<-gtrends("visa Germany",geo=c("IQ"),hl='ar',time='2005-01-01 2018-01-01', onlyInterest = TRUE)
IQ_GE_biv.1 <- IQ_GE_biv.1 %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])

IQ_GE_biv.2<-gtrends("work Germany",geo=c("IQ"),hl='ar',time='2005-01-01 2018-01-01', onlyInterest = TRUE)[[1]]
IQ_GE_biv.2 <- IQ_GE_biv.2 %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==

IQ_GE_biv.3<-gtrends("immigration",geo=c("IQ"),hl='ar',time='2005-01-01 2018-01-01', onlyInterest = TRUE)[[1]]

IQ_GE_biv.3 <- IQ_GE_biv.3 %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])
IQ_GE_biv.3

IQ_GE_cat<-gtrends("germany",geo=c("IQ"),hl='ar', category=555, time='2005-01-01 2018-01-01', onlyInterest = TRUE)[[1]]
IQ_GE_cat <- IQ_GE_cat %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, keyword, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])
IQ_GE_cat
```

```{r}
#add all to one data frame
#destinationn, univariate,bivariate
data<-merge(GT_IQ_GE_year_1,IQ_GE_year_1, by='Year')%>% merge(IQ_GE_cat,by="Year")

data
#'germany','immigration'
data.agg<-data%>%select(Year,hits_average.x,hits_average.y,hits_average)

#this is the average of bivariate,univariate, and destination
sum.data<-data.agg%>%
  group_by(Year)%>%
  summarise(sum=(hits_average.x + hits_average.y+hits_average))


#comparing with historic data
p <- ggplot(data=Iraq_Germany, aes(x=Year)) +
  geom_line(aes(y=Value),color = "blue", group = 1) +
  labs(y="Migration Inflow")
# GT data
q <- ggplot(data=sum.data, aes(x=Year)) +
  geom_line(aes(y = sum), color = "red",group = 1) +
  labs(y = "Yearly search hits")

ggarrange(p, q, 
          labels = c("Migration flow", "Search hits"),
          ncol = 1, nrow = 2)

p
```
```{r}

```
#when we obtain for just the category.
```{r}
#just the Category...
IQ_GE_cat<-gtrends(geo=c("IQ"), category=555, time='2005-01-01 2018-01-01', onlyInterest = TRUE)
IQ_GE_cat
plot(IQ_GE_cat)
IQ_GE_cat <- IQ_GE_cat$interest_over_time %>%  mutate(Year = str_extract(date, "^.{4}")) %>% group_by(Year, geo) %>%
  summarise(hits_average = mean(hits)) %>% 
  mutate(category = Cat_interest[which(Cat_interest$id ==
                                         555),][[1]])
IQ_GE_cat
```

#comparing with historic data
```{r}

IQ_GE_cat <- IQ_GE_cat %>%  filter(Year != 2018) %>% 
  ungroup() %>% 
  select(Year, hits_average)

#comparing with historic data
p <- ggplot(data=Iraq_Germany, aes(x=Year)) +
  geom_line(aes(y=Value),color = "blue", group = 1) +
  labs(y="Migration Inflow")
# GT data
q <- ggplot(data=IQ_GE_cat, aes(x=Year)) +
  geom_line(aes(y =hits_average), color = "red",group = 1) +
  labs(y = "Yearly search hits")
p
```
```{r}
#no search term just category
q
```
# Aggregate with just catagory and germany
# Catagory and destination
```{r}
#merge with catagory,destination,
cat_dest_data<-merge(IQ_GE_cat,GT_IQ_GE_year_1, by= 'Year')
#cat_dest_data

av_cat_des_data <-cat_dest_data%>%
  group_by(Year)%>%
  summarise(average=(hits_average.x + hits_average.y)/2)

q <- ggplot(data=av_cat_des_data, aes(x=Year)) +
  geom_line(aes(y =average), color = "red",group = 1) +
  labs(y = "Yearly search hits")
q
```
# aggregating with category destination and univariate case
```{r}

merged<-merge(cat_dest_data,IQ_GE_biv.3,by= 'Year')

av_cat_des_uni_data <-merged%>%
  group_by(Year)%>%
  summarise(average=(hits_average.x + hits_average.y+hits_average)/3)

q <- ggplot(data=av_cat_des_uni_data, aes(x=Year)) +
  geom_line(aes(y =average), color = "red",group = 1) +
  labs(y = "Yearly search hits")
q
```
```{r}
IQ_GE_cat<-gtrends(geo=c("IQ"),category = 1313, time='2005-01-01 2018-01-01', onlyInterest = TRUE)
plot(IQ_GE_cat)
```

